---
title: "Untitled"
author: "Eivind Vinsand,"
date: "2 12 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse) # For a tidyer code
library(BatchGetSymbols) # Get Stock data from Yahoo
library(formattable) # Format as percent
library(scales) # To format number as millions
library(shiny)
library(quantmod)
library(highcharter)
library(shinythemes)
library(reactable)
library(tbl2xts)
library(argonDash)
```

Problem description

In this script, we will create a dynamic shiny app. The app will include a dashboard with a range of
different stock related statistics. It will have compelling visualizations and
possibility to interact with the data. Furthermore, we would like to create an
option for the user to select different stocks to a portfolio and see how this
portfolio has performed in a user-selected period.

The script is divided into X parts:
1. Webscraping ticker and company names
2. Fetching stock data from Yahoo Finance
3. Creating content for
4. XXX



Part 1: Webscraping ticker and company names

We will use webscraping to get the tickers and company names for all Norwegian stocks. The ticker and company names will be scraped from gurufocus.com.
Since only 100 stocks are displayed per page, we need to:
a) Find out how many pages to scrape
b) Get the URL for each page
c) Scrape all the pages
d) cleaning the data


```{r, 1a) - Find out how many pages to scrape}
# First page of stocks
base_url = "https://www.gurufocus.com/stock_list.php?m_country[]=NOR&p=50&p=0&n=100" 

# CSS element for number of Norwegian stocks listed 
total_records_selector = "#ajax_content strong" 

# Scraping total number of stocks listed on the page
total_records <- read_html(base_url) %>% 
  html_nodes(total_records_selector) %>% 
  html_text()

# Calculating number of pages to scrape (Number of stocks/100 stocks per page)
total_pages <- ceiling(as.numeric(head(total_records,1))/100) # Total number of pages

cat("Total pages to scrape:",total_pages)
```


```{r, 1b) - Get the URL for each page}
# Creating a vector of page numbers
page_vector <- c(0:(total_pages-1)) 

# Splitting base URL into two parts (excluduing page number)
url1 = "https://www.gurufocus.com/stock_list.php?m_country[]=NOR&p=50&p="
url2 = "&n=100"

# Generating URL for each page to scrape
for (page in page_vector){
  url <- paste(url1,page_vector,url2, sep ="") # Creating URL
  url_list <- url #Adding URL to list
}

url_list # List of URLs to scrape
```


```{r , 1c) - Scrape all the pages}
# CSS Element for ticker name and company name
ticker_selector = ".text .nav" # CSS selector
company_selector = ".text+ td a" # CSS selector

# Creating an empty tibble to store data in
stock_data <- tibble(tickers = as.character(),
                     company_name = as.character())

# Scraping ticker and company names
for(i in seq_along(url_list)){
  
  tickers <- read_html(url_list[i]) %>% 
  html_nodes(ticker_selector) %>%
  html_text()
  
  company_name <- read_html(url_list[i]) %>% 
  html_nodes(company_selector) %>%
  html_text()
  
  stock_data <- stock_data %>% 
    add_row(tickers = tickers,
            company_name = company_name)
}

stock_data
```


```{r, 1d) - Cleaning the data}
stock_data <- stock_data[grepl('Norway', stock_data$tickers), ] # Removing redundant rows
yahoo_tickers <- str_replace(stock_data$tickers,"Norway", "OL" ) # Formating tickers to Yahoo format

stock_data <- stock_data %>% transmute(ticker = yahoo_tickers,
                                    company_name = company_name)  # Replacing tickers with Yahoo tickers
stock_data
```

Part 2: Fetching stock data from Yahoo Finance

To get historical stock data about our stocks, we will use the quantmode package to extract data  from Yahoo Finance. We will use the BatchGetSymbols function to get the stock data in a more tidy format.


```{r, 2 - Loading Stock data, include=FALSE}
start_date <- Sys.Date() - 365 # First date of data to retrieve 
end_date <- Sys.Date()  # Last date of data to retrieve

portfolio_data <- BatchGetSymbols(tickers = stock_data$ticker,
                         first.date = start_date,
                         last.date = end_date,
                         freq.data = "daily",
                         bench.ticker = "^OSEBX",
                         cache.folder = file.path(tempdir(),
                                                  'BGS_Cache') ) # cache in tempdir()
benchmark_data <- getSymbols.yahoo("^OSEBX",
                             first.date = start_date,
                             last.date = end_date,
                             auto.assign=FALSE)

portfolio_data2 <- portfolio_data$df.tickers

  
```

```{r}
hchart(benchmark_data, type = "ohlc") %>% 
  hc_add_theme(hc_theme_db())


```

Part 3: Creating tables for the dashboard
 We want to create four tables showing daily data of:
 a) The most traded stocks
 b) Winners
 c) Loser
 d) Hot Stocks (Stocks with volume anomaly)


```{r, 3 - Creating data tables}
last_data <- portfolio_data2
last_data[last_data==0] <- NA
last_data <- subset(last_data, startsWith(as.character(ref.date), "2020"))
last_data <- last_data%>%
  group_by(ticker) %>%
  mutate(AvgVolume = mean(volume*price.close)) %>% 
  summarise_all(last)
last_data <- left_join(last_data, stock_data, by = "ticker") 

market_data <- last_data %>%
  transmute(Company = company_name,
            Last = price.close,
            High = price.high,
            Low = price.low,
            "+/- %" = (price.close-price.open)/price.open,
            "+/- NOK" = (price.close-price.open),
            Volume = volume*price.close)
  
  
last_data <-   last_data %>% 
  transmute(Company = company_name,
            "+/- %" = (price.close-price.open)/price.open,
            Last = price.close,
            Volume = volume*price.close,
            AvgVolume = AvgVolume)

# a) The most traded stocks
top_vol <- last_data[-5]%>% 
  arrange(desc(last_data$Volume)) %>% 
  mutate(Volume = unit_format(unit = 'M', scale = 1e-6, digits =2)(Volume),
         `+/- %` = percent(`+/- %`))%>% 
  head(10)
top_vol

# b) Winners
winners <- last_data[-5] %>% 
  arrange(desc(last_data$`+/- %`)) %>% 
  mutate(Volume = unit_format(unit = 'M', scale = 1e-6, digits =2)(Volume),
         `+/- %` = percent(`+/- %`))%>% 
  head(10)
winners

# c) Losers
losers <- last_data[-5] %>% 
  arrange(last_data$`+/- %`) %>% 
  mutate(Volume = unit_format(unit = 'M', scale = 1e-6, digits =2)(Volume),
         `+/- %` = percent(`+/- %`))%>% 
  head(10)
losers


#d) Hot Stocks
hot_stock <- last_data %>% 
  mutate(Ratio = Volume/AvgVolume) %>% 
  arrange(desc(Ratio)) %>% 
  mutate(Volume = unit_format(unit = 'M', scale = 1e-6, digits =2)(Volume),
         Ratio = percent(Ratio)) %>% 
  head(10)
hot_stock <- hot_stock[c(1,3,6)]
hot_stock

```

```{r, Portfolio maker}
# Users selected stocks
my_stocks <- c("Norwegian Air Shuttle ASA", "Havila Shipping ASA", "Axactor SE") 

#Users Stocks
cost_price <- c(2,2,2) # Users cost price
quantity <- c(409, 14, 30) # Users quantity


# Table for your stock portfolio overview
my_portfolio <- last_data[last_data$Company %in% my_stocks, ][-5] %>%
  transmute(Company = Company,
         `Cost Price` = cost_price,
         Quantity = quantity,
         `Market Price` = Last,
         `Market Value` = Last*quantity,
         `Profit (%)` = percent((Last-cost_price)/cost_price),
         `Weight (%)` = percent(`Market Value`/sum(`Market Value`)))
         
my_portfolio


# Create a pie chart of the portfolio weights
# weights_pie <- my_portfolio%>% 
#   hchart("pie", hcaes(x = Company, y = `Weight (%)`)) %>% 
#   hc_title(text = "Axactor Stock Price")
#     
# 
# weights_pie

```



```{r, Plotting chart for each stock}

# Spliting the stock data into a list of data frames for each stock
stock_list <- portfolio_data2 %>%
  rename(date = ref.date) %>%
  split(portfolio_data2 , f = portfolio_data2$ticker)


# Creating xts object for a stocks historical data
plot_data <- as.data.frame(stock_list[["AXA.OL"]]) %>%
tbl_xts()


# Creating highcharter plot using the xts object
plot <- hchart(plot_data, type = "ohlc") %>%
  hc_title(text = "Axactor Stock Price") %>%
  hc_add_theme(hc_theme_db())
plot


# NB! Here we should create a function that creates a plot for
# selected stocks (maybe a hyperlink on each stock name in the list will bring us
# to a page of stock name, historical profit and a the price plot, beta, alpha etc.)


```



