---
title: "BAN400 - Exam"
author: "Candidates: 	17, 73, 34"
date: "2 12 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Loading libraries
library(tidyverse)       # For a tidyer code
library(BatchGetSymbols) # Get Stock data from Yahoo
library(formattable)     # Formatting library
library(scales)          # Formatting library
library(shiny)           # To create Shiny App
library(shinydashboard)  # To create Shiny Dashboard
library(quantmod)        # Financtial data library
library(highcharter)     # MInteractive plots
library(reactable)       # Ineractive tables
library(tbl2xts)         # Format fromt table to xts object

```

Problem description

In this script, we will create a dynamic shiny app. The app will include a dashboard with a range of
different stock related statistics. It will have compelling visualizations and
possibility to interact with the data. Furthermore, we would like to create an
option for the user to select different stocks and see a plot of historical prices.

The script is divided into 6 parts:
1. Webscraping ticker and company names
2. Fetching stock data from Yahoo Finance
3. Creating data tables & plots for the app
4. Shiny Dashboard frontend
5. Shiny Dashboard backend


Part 1: Webscraping ticker and company names

We will use webscraping to get the tickers and company names for all Norwegian stocks. The ticker and company names will be scraped from gurufocus.com. Since only 100 stocks are displayed per page, we need to:
a) Find out how many pages to scrape
b) Get the URL for each page
c) Scrape all the pages
d) Clean the data to match Yahoo Finance tickers


```{r, 1a) - Find out how many pages to scrape}
# First page of stocks
base_url = "https://www.gurufocus.com/stock_list.php?m_country[]=NOR&p=50&p=0&n=100" 

# CSS element for number of Norwegian stocks listed 
total_records_selector = "#ajax_content strong" 

# Scraping total number of stocks listed on the page
total_records <- read_html(base_url) %>% 
  html_nodes(total_records_selector) %>% 
  html_text()

# Calculating number of pages to scrape (Number of stocks/100 stocks per page)
total_pages <- ceiling(as.numeric(head(total_records,1))/100) # Total number of pages

cat("Total pages to scrape:",total_pages)
```


```{r, 1b) - Get the URL for each page}
# Creating a vector of page numbers
page_vector <- c(0:(total_pages-1)) 

# Splitting base URL into two parts (excluduing page number)
url1 = "https://www.gurufocus.com/stock_list.php?m_country[]=NOR&p=50&p="
url2 = "&n=100"

# Generating URL for each page to scrape
for (page in page_vector){
  url <- paste(url1,page_vector,url2, sep ="") # Creating URL
  url_list <- url #Adding URL to list
}

url_list # List of URLs to scrape
```


```{r , 1c) - Scrape all the pages}
# CSS Element for ticker name and company name
ticker_selector = ".text .nav" # CSS selector
company_selector = ".text+ td a" # CSS selector

# Creating an empty tibble to store data in
stock_data <- tibble(tickers = as.character(),
                     company_name = as.character())

# Scraping ticker and company names
for(i in seq_along(url_list)){
  
  # Scraping tickers
  tickers <- read_html(url_list[i]) %>% 
  html_nodes(ticker_selector) %>%
  html_text()
  
  # Scraping company names
  company_name <- read_html(url_list[i]) %>% 
  html_nodes(company_selector) %>%
  html_text()
  
  # Addubg data to the stock_data tibble
  stock_data <- stock_data %>% 
    add_row(tickers = tickers,
            company_name = company_name)
}

stock_data
```


```{r, 1d) - Cleaning the data}
#
stock_data <- stock_data[grepl('Norway', stock_data$tickers), ] # Removing redundant rows
yahoo_tickers <- str_replace(stock_data$tickers,"Norway", "OL" ) # Formatting tickers to Yahoo ticker format for OSEBX

stock_data <- stock_data %>% transmute(ticker = yahoo_tickers,
                                    company_name = company_name)  # Replacing tickers with Yahoo tickers
stock_data
```

Part 2: Fetching stock data from Yahoo Finance

To get historical stock data about our stocks, we will use the quantmode/BatchGetSymbols package to extract data from Yahoo Finance. We will use the BatchGetSymbols function to get the stock data in a more tidy format. 


```{r, 2 - Loading Stock data, include=FALSE}
start_date <- Sys.Date() - 365 # First date of data to retrieve 
end_date <- Sys.Date()  # Last date of data to retrieve

# Fetching historical stock data for 1 year into portfolio_data.
# This function takes about 5 minutes to load. The progression can be seen in the console!
# If you want less loading time, you can change the start_date above (E.g. Sys.Date() - 7)!
portfolio_data <- BatchGetSymbols(tickers = stock_data$ticker,
                         first.date = start_date,
                         last.date = end_date,
                         freq.data = "daily",
                         bench.ticker = "^OSEBX",
                         cache.folder = file.path(tempdir(),
                                                  'BGS_Cache') ) # cache in tempdir()

# Fetching data for the benchmark OSEBX. Using getSymbols here since we only need xts format.
benchmark_data <- getSymbols.yahoo("^OSEBX",
                             first.date = start_date,
                             last.date = end_date,
                             auto.assign=FALSE)

# Adding the data frame we want from BatchGetSymbols into a new data frame called portfolio_data2
portfolio_data2 <- portfolio_data$df.tickers

  
```


Part 3: Creating tables & plots for the dashboard
 We want to create four tables showing daily data of:
 a) The most traded stocks
 b) Winners
 c) Loser
 d) Hot Stocks (Stocks with volume anomaly)
 In addition, we want a data frame for the complete stock list and a function to plot charts for historical prices.


```{r, 3 - Creating data tables}
# Creating a new data frame with the data for the last trading day 
last_data <- portfolio_data2 
last_data[last_data==0] <- NA # Replacing 0 with NA
#last_data <- subset(last_data, startsWith(as.character(ref.date), "2020"))
last_data <- last_data%>%
  group_by(ticker) %>%
  mutate(AvgVolume = mean(volume*price.close)) %>% 
  summarise_all(last)
last_data <- left_join(last_data, stock_data, by = "ticker") 

# Creating data table for full stock list
market_data <- last_data %>%
  transmute(Company = company_name,
            Last = price.close,
            High = price.high,
            Low = price.low,
            "+/- %" = (price.close-price.open)/price.open,
            "+/- NOK" = (price.close-price.open),
            Volume = volume*price.close)
  
# Transmuting the data frame used to create the tables below 
last_data <-   last_data %>% 
  transmute(Company = company_name,
            "+/- %" = (price.close-price.open)/price.open,
            Last = price.close,
            Volume = volume*price.close,
            AvgVolume = AvgVolume)

# a) The most traded stocks
top_vol <- last_data[-5]%>% 
  arrange(desc(last_data$Volume)) %>% 
  mutate(Volume = unit_format(unit = 'M', scale = 1e-6, digits =2)(Volume),
         `+/- %` = percent(`+/- %`))%>% 
  head(10)
top_vol

# b) Winners
winners <- last_data[-5] %>% 
  arrange(desc(last_data$`+/- %`)) %>% 
  mutate(Volume = unit_format(unit = 'M', scale = 1e-6, digits =2)(Volume),
         `+/- %` = percent(`+/- %`))%>% 
  head(10)
winners

# c) Losers
losers <- last_data[-5] %>% 
  arrange(last_data$`+/- %`) %>% 
  mutate(Volume = unit_format(unit = 'M', scale = 1e-6, digits =2)(Volume),
         `+/- %` = percent(`+/- %`))%>% 
  head(10)
losers


#d) Hot Stocks
hot_stock <- last_data %>% 
  mutate(Ratio = Volume/AvgVolume) %>% 
  arrange(desc(Ratio)) %>% 
  mutate(Volume = unit_format(unit = 'M', scale = 1e-6, digits =2)(Volume),
         Ratio = percent(Ratio)) %>% 
  head(10)
hot_stock <- hot_stock[c(1,3,6)]
hot_stock



```



```{r, Plotting chart for each stock}

# Spliting the stock data into a list of data frames for each stock
stock_list <- portfolio_data2 %>%
  rename(date = ref.date) %>%
  split(portfolio_data2 , f = portfolio_data2$ticker)


# Function that turns a stocks historical data into xts and creates a highcharter price chart.
plot_stock <- function(company){
  index <- company %>% match(stock_data$company_name) # Finding the company's position in stock_data
  stock_to_plot <- stock_data$ticker[index]           # Getting the companys ticker name 
  chart_name <-  paste(company)                       # Name of plot
  
  # Transforming the stocks historical data into an xts object
  plot_data <- as.data.frame(stock_list[[stock_to_plot]]) %>% 
tbl_xts()
  
  # Creating a higcharter interactive plot of the historical stock prices
  plot <- hchart(plot_data, type = "ohlc") %>%
    hc_title(text = chart_name) %>% 
  hc_add_theme(hc_theme_smpl())
plot
  
}




```

Part 4: Shiny Dashboard frontend

```{r, Shiny App frontend}
ui <- dashboardPage(
  # Theme color
  skin = "purple",
  
  # Header
  dashboardHeader(title = "Stockmate"),
  
  # Sidebar content
  dashboardSidebar(sidebarMenu(
    menuItem("Dashboard", tabName = "dashboard", icon = icon("landmark")),
    menuItem("Price Plotter", tabName = "price_plot", icon = icon("hand-holding-usd"))
    )),
  
  # Body content
  dashboardBody(
    tabItems(
      
      # Dashboard content
      tabItem(tabName = "dashboard",
              h2("Market overview"),
              
              
              tabBox(width = 12,
                     
              # Market Overview tab
              tabPanel("Market Overview",
              fluidRow(
                   column(4, width = 12,
                        h3 ("Oslo Stock Exchange"),
                        highchartOutput("hc3"))),
              fluidRow(
                  # Winners table
                  column(4, 
                         width = 6,
                         length = 5,
                         h3("Winners"),
                         reactableOutput('winners')),
                  # Losers table
                  column(6, 
                         width = 6,
                         length = 5,
                         h3("Losers"),
                         reactableOutput('losers'))),
              fluidRow( 
                  # Most bought table
                  column(4,
                         width = 6,
                         length = 5,
                         h3("Most Bought"),
                         reactableOutput('top_vol')),
                  
                  # Stocks with abnormal volume table
                  column(6, 
                         width = 6,
                         length = 5,
                         h3("Hot Stock - Abnormal volume"),
                         reactableOutput('hot_stock')))),
            
              # Stock List tab
              tabPanel("Stock List",
                       fluidRow(
                         column(4,
                                width = 12,
                                reactableOutput('stock_list'))
                       ))
              
              
              )),

    # Price plot content
    tabItem(tabName = "price_plot",
            h2("Historical Price Plot"),
            fluidRow(
              
              # Selactable list of stocks to plot
              column(4,
                     width = 12,
           selectizeInput("stock", "Stock To Plot", last_data$Company , selected = NULL, multiple = FALSE,
          options = list(create = TRUE)),
           highchartOutput("plot")
         
    )))
    )
    )
  )
  





```

Part 5: Shiny Dashboard backend

```{r, Shiny App backend}
# Conditional color function to format positive returns green, and negative red.
color_function <- function(value) {
  if (value > 0) {
    color <- "#008000"
  } else if (value < 0) {
    color <- "#e00000"
  } else {
    color <- "#777"
  }
  list(color = color, fontWeight = "bold")
}


# Shiny Dashboard Server

server <- function(input, output) {
  
      # Winners table
      output$winners <- renderReactable({
        reactable(winners,
                  defaultPageSize = 10,
                  columns = list(
                    Last = colDef(format = colFormat(digits = 2)),
                    `+/- %` = colDef(style = color_function)
                    
                  ))
      })
      
      # Losers table
      output$losers <- renderReactable({
        reactable(losers,
                  compact = TRUE,
                  defaultPageSize = 10,
                  columns = list(
                    Last = colDef(format = colFormat(digits = 2)),
                    `+/- %` = colDef(style = color_function)
                    
                  ))
      })
      # Top Volume table
      output$top_vol <- renderReactable({
        reactable(top_vol,
                  compact = TRUE,
                  defaultPageSize = 10,
                  columns = list(
                    Last = colDef(format = colFormat(digits = 2)),
                    `+/- %` = colDef(style = color_function)
                    
                  ))
      })
      # Hot Stocks table
      output$hot_stock <- renderReactable({
        reactable(hot_stock,
                  compact = TRUE,
                  defaultPageSize = 10,
                  columns = list(
                    Last = colDef(format = colFormat(digits = 2)),
                    Ratio = colDef(style = color_function)
                    
                  ))
      })
      
      # OSEBX Price Plot
      output$hc3<-renderHighchart({
        hchart(benchmark_data, type = "ohlc") %>%
        hc_add_theme(hc_theme_smpl())
      })
      
      # Stock Price Plot
      output$plot <- renderHighchart({
        plot_stock(input$stock)
      })
      
      
      # Stock list
      output$stock_list <- renderReactable({
        reactable(market_data,
                  
                  #Number of rows per page
                  defaultPageSize = 12,
                  
                  # Making the table searchable
                  searchable = TRUE,
                  
                  # Default sorting
                  defaultSorted = "Volume",
                  
                  # Column formatting
                  columns = list(
                    Last = colDef(format = colFormat(digits = 2)),
                    High = colDef(format = colFormat(digits = 2)),
                    Low = colDef(format = colFormat(digits = 2)),
                    Volume = colDef(defaultSortOrder = "desc",
                                    format = colFormat(digits = 0)),
                    
                    #Conditional formatting
                    
                    `+/- %` = colDef(style = color_function,
                    format = colFormat(percent = TRUE, digits = 2)),
                    
                    `+/- NOK` = colDef(style = color_function,
                                       format = colFormat(digits = 2))
                  )
        )
                    
                    
                    

                 
      })
      


}

shinyApp(ui, server)
```

